---
output:
  html_document:
    highlight: null
    css: style.css
    self_contained: no
    keep_md: true
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(stringr)

date <- "10/11/2018"
vendor <- "Cedars Mediterranean Kitchen"
title <- "The fractal brain and cognitive effort"
file_title <- "Suppression of Scale Free fMRI Brain Dynamics"
short_title_n = 3
speaker <- "Marc Berman"
department <- "Assistant Professor of Psychology and the Director of the Environmental Neuroscience Laboratory"
university <- "The University of Chicago"
github_home <- "https://github.com/uchicago-computation-workshop"


```

```{r, echo=FALSE}
#Function to Shorten Title
small_title <- function(x, n=3) {
  ul <- unlist(strsplit(x, split = "\\s+"))[1:n]
  paste(ul,collapse=" ")
}

#Characters
unwanted_array = list(    'Š'='S', 'š'='s', 'Ž'='Z', 'ž'='z', 'À'='A', 'Á'='A', 'Â'='A', 'Ã'='A', 'Ä'='A', 'Å'='A', 'Æ'='A', 'Ç'='C', 'È'='E', 'É'='E',
                            'Ê'='E', 'Ë'='E', 'Ì'='I', 'Í'='I', 'Î'='I', 'Ï'='I', 'Ñ'='N', 'Ò'='O', 'Ó'='O', 'Ô'='O', 'Õ'='O', 'Ö'='O', 'Ø'='O', 'Ù'='U',
                            'Ú'='U', 'Û'='U', 'Ü'='U', 'Ý'='Y', 'Þ'='B', 'ß'='Ss', 'à'='a', 'á'='a', 'â'='a', 'ã'='a', 'ä'='a', 'å'='a', 'æ'='a', 'ç'='c',
                            'è'='e', 'é'='e', 'ê'='e', 'ë'='e', 'ì'='i', 'í'='i', 'î'='i', 'ï'='i', 'ð'='o', 'ñ'='n', 'ò'='o', 'ó'='o', 'ô'='o', 'õ'='o',
                            'ö'='o', 'ø'='o', 'ù'='u', 'ú'='u', 'û'='u', 'ý'='y', 'ý'='y', 'þ'='b', 'ÿ'='y' )


#Year
year <- substr(date, nchar(date)-4+1, nchar(date))

#Author Name
author_clean_lower <- str_replace_all(str_to_lower(speaker), " ", "_")

#Remove Unwanted Characters
out <- author_clean_lower
for(i in seq_along(unwanted_array))
    out <- gsub(names(unwanted_array)[i],unwanted_array[i],out)
author_clean <- out
author_lastname <- tail(strsplit(author_clean,split="_")[[1]],1)

#Repository Name
#repo = paste(year, author_clean, sep = "_")
repo = author_clean
issues_page <- paste(github_home, repo, "issues", sep="/")
repo_page <- paste(github_home, repo, sep="/")

#Create File Name Parts
short_title <- small_title(file_title, short_title_n)
paper_file <- paste(year, author_lastname, short_title, sep="  ")

#Clean Up File Name
punct <- '[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]'

#Remove Punctuation
lowered_name <- str_to_lower(paper_file)
stripped_name <- str_replace_all(lowered_name, punct, "")
cleaned_name <- str_replace_all(stripped_name, " ", "_")
cleaned_paper_file <- paste(cleaned_name, "pdf", sep=".")

#File Name Link
paper_link = paste(github_home, repo, "blob/master", cleaned_paper_file, sep="/"  )


#Clean Short Title
short_title_clean <- str_replace_all(short_title, punct, "")

```

<br>

<h3 class=pfblock-header> The Computational Social Science Workshop Presents </h3>

<h1 class=pfblock-header3> `r speaker` </h1>
<h3 class=pfblock-header3> `r department` </h3>
<h3 class=pfblock-header3> `r university` </h3>

<br><br>



<p class=pfblock-header3>The <a href="https://macss.uchicago.edu/content/computation-workshop"> Computational Social Science Workshop </a> at the University of Chicago cordially invites you to attend this week's talk:</p>

<br>

<div class=pfblock-header3>
<h2 class=pfblock-header>
  <a href="https://github.com/uchicago-computation-workshop/marc_berman/blob/master/2018_berman_suppression_of_scale.pdf"> The Fractal Brain and Cognitive Effort </a>
</h2>

<br>
</div>

<p class=footertext2>

**Summary:** Cognitive effort is often easily experienced and yet hard to define.  Is the cognitive effort of learning a new task related to the cognitive effort of having to remember and manipulate more items in memory?  What about the increased cognitive effort that accompanies aging or physical and mental illness.  Here I present a theory that cognitive effort is related to the fractal scaling of brain hemodynamics (as measured with fMRI) and with the fractal scaling of the brains electrical activity (as measured with EEG).  From analyzing a number of datasets that manipulated cognitive effort in a number of ways, we find consistently that higher fractal scaling is associated with decreased cognitive effort.  This work could help to identify biological markers that index how much cognitive effort an individual is exerting.

</p>

<br>



<h4 class=pfblock-header3> Thursday, `r date` </h4>
<h4 class=pfblock-header3> 11:00am-12:20pm </h4>
<h4 class=pfblock-header3> Kent 120 </h4>

<br>

<p class=pfblock-header3>A light lunch will be provided by `r vendor`.</p>

<br><br>

<p class=footertext2>

**`r speaker`** is an Assistant Professor of Psychology and is the Director of the Environmental Neuroscience Laboratory at the University of Chicago.  In his research he applies novel statistical and computational models to quantify brain networks and applies those metrics to broader psychological phenomena such as self-control, depression, anxiety and cognitive effort.  He and his lab are also interested in quantifying the physical and social environment to better understand brain-environment interactions and how those interactions can be used to understand human behavior.  In particular, Berman and his team are trying to understand why natural environments have beneficial effects on body and mind.  Berman received his Ph.D. in Cognitive Neuroscience and Industrial and Operations Engineering from the University of Michigan in 2010.  He is the recipient of the 2018 Association for Psychological Science’s (APS) Early Career Research Award and the Neubauer Faculty Development Fellowship for excellence in teaching and mentorship.  His work has been featured in many publications including the Atlantic Monthly, the New York Times, the New Yorker, the Boston Globe, Chicago Magazine, the Toronto Star and the Wall Street Journal.
</p>

<br>


<br><br>

---

<p class=footertext> The 2018-2019 <a href="https://macss.uchicago.edu/content/computation-workshop"> Computational Social Science Workshop </a> meets each Thursday from 11 a.m. to 12:20 p.m. in Kent 120. All interested faculty and graduate students are welcome.</p>

<p class=footertext>Students in the Masters of Computational Social Science program are expected to attend and join the discussion by posting a comment on the <a href="`r issues_page`"> issues page </a> of the <a href="`r repo_page`"> workshop's public repository on GitHub.</a> Further instructions are documented in the Computational Social Science Workshop's <a href="https://github.com/uchicago-computation-workshop/README"> README on Github.</a></p>
